Hybrid Threads for the Parrot Virtual Machine

### 2012-03-29 Paper.tex
Mention the first test program

>>>>

In addition to Parrot's extensive test suite, tests were conducted using three test programs.

\section{tasks.pir}

tasks.pir is a simple test program, executing two \textit{Tasks} called ``a'' and ``b'' which run in tight loops printing their name on each 100000th iteration. The program ends after running for 10 seconds. This is a test of thread creation and task scheduling but does not access any shared data. The full code is as follows:
%
\begin{GenericCode}
.sub main :main
    .local pmc task, a, b, a_task, b_task
    task = get_global 'task'
    a = new ['String']
    a = "a"
    b = new ['String']
    b = "b"
    a_task = new ['Task']
    setattribute a_task, 'code', task
    setattribute a_task, 'data', a
    b_task = new ['Task']
    setattribute b_task, 'code', task
    setattribute b_task, 'data', b
    schedule a_task
    schedule b_task
    sleep 10
    exit 0
.end

.sub task
    .param pmc name
    .local int i
start:
    print name
    i = 0
loop:
    inc i
    if i >= 100000 goto start
    goto loop
.end
\end{GenericCode}
